Attrition in Online Learning: Understanding Persistence and Dropout in Massive Open Online Courses

### 2014-10-17 paper_v1.Rnw
more work on lit. review

A survey of over one hundred learners who dropped out of MOOC showed that most learners indicated too little time due to work responsibilities, not enough social support inside and outside of the course, and insufficient academic and technical support from the course \cite{gutl2014attrition}. A qualitative analysis of public records, especially forum posts, from 42 MOOCs suggested the following reasons for attrition: lack of time, learner motivation, feelings of isolation, lack of interactivity, insufficient prior knowledge or skills, and hidden costs \cite{khalil2014moocs}. A survival analysis of close to 800 learners who had posted on a MOOC discussion forum suggested that i. the likelihood of dropout was lower for those who actively participated in the first week of the course; ii. those who served as an authority figure in the community on the forum, and iii. those who did not engage in a particular subcommunity on the forum \cite{yang2013turn}. In addition, a number of machine learning approaches to predicting attrition yielded promising results (e.g. \cite{taylor2014likely,halawa2014dropout}), but fell short of offering insight into why a given learner left the course.

>>>>

A survey of over one hundred learners who dropped out of MOOC showed that most learners indicated too little time due to work responsibilities, not enough social support inside and outside of the course, and insufficient academic and technical support from the course \cite{gutl2014attrition}. A qualitative analysis of public records, especially forum posts, from 42 MOOCs suggested the following reasons for attrition: lack of time, learner motivation, feelings of isolation, lack of interactivity, insufficient prior knowledge or skills, and hidden costs \cite{khalil2014moocs}. Based on just over one thousand learners who participated in the discussion forum of a particular MOOC, the likelihood of dropout was lower for those who actively participated in the first week of the course, those who served as an authority figure in the community on the forum, and those who did not engage in a particular subcommunity on the forum \cite{rose2014social}.

A number of machine learning approaches to predicting attrition have been tested, incluging hidden Markov models \cite{balakrishnan2013predicting},

### 2014-10-17 paper_v1.tex
more work on lit. review

A number of machine learning approaches to predicting attrition yielded promising results, e.g. \cite{taylor2014likely,halawa2014dropout}, but fell short of offering insight into why a given learner left the course.

>>>>

A number of machine learning approaches to predicting attrition have been tested, incluging hidden Markov models \cite{balakrishnan2013predicting},
